### 2012-11-25 paper.tex
tables floatbarrier

	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     		&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 0 & 93\\
\hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}

@@

	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     					&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 0 & 93\\
\hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 1 & 92\\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:echo:bayes:1c}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 3 & 1 \\
b=1 & 9 & 84\\
\hline
\end{tabular}
\caption{Confusion matrix for kNN}
\label{tab:echo:bayes:2c}
\end{table}

\paragraph{}Also the detailed accuracy table \ref{tab:echo:bayes:2d} shows that this approach gained a high recall with a low precision for alive-at-1 = 0 and both high precision and recall for alive-at-1 = 1.

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure \\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

@@

	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
              &    a &     b \\
\hline
 a = >50k      & 4454 &  3387 \\
 b = $\leq$50k & 1531 & 23189\\
\hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
              &    a &     b \\
\hline
 a = >50k      & 6321 &1520   \\
 b = $\leq$50k & 4025 &20695 \\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:adult:bayes:1c}
\end{table}

\paragraph{}By using different discretizers and also do not seperately discretize in the preprocessing section of weka but instead let the NaiveBayers classifier use it's own discretizers namely KernelEstimator or SupervisedDiscretizer the outcome of precision and recall differ a bit by 0.05 to 0.1 higher and lower. It does obviously do not really make a difference.

@@

	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831     \\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
	\hline
	 &              a    & b     \\
	\hline
    a = >50K      &	4647 & 3194  \\
    b = $\leq$50K & 2186 & 22534 \\
    \hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure  \\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     \\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851    \\
  Naive Bayes		 	&  0.83    & 0.186   & 0.854     & 0.83   & 0.837     \\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     \\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831			\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	    	&3\\
	Weighted Avg.   &0.492     	&0.28      &0.491     	&0.492   &0.491     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
	\hline
	      &a   &b   &c \\
	\hline
	a = 1 &367 &105 &157 \\
 	b = 2 &117 &131 &85 \\
 	c = 3 &183 &101 &227 \\
  \hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}

@@

	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      				&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}

\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
	\hline
	      &a   &b   &c \\
	\hline
    a = 1 &358 &99  &172\\
    b = 2 &99  &138 &96 \\
 	c = 3 &197 &90  &224 \\
  \hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
\hline
              &   a &   b &   c  \\
\hline
 a = 1        & 327 & 141 & 161  \\
 b = 2        &  61 & 175 &  97  \\
 c = 3        & 127 & 138 & 246  \\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:contra:bayes:1c}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   \\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     \\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     \\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     	& 0.508  & 0.513 \\
  SVM							& 0.492    &0.280     &0.491     	&0.492   & 0.491 		 \\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\bibliography{references}

>>>>

	Weighted Avg.		&0.959     	&0.959     &0.919   		&0.959   &0.939     		&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the echocardiogram dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 0 & 93\\
\hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}
\FloatBarrier

@@

	Weighted Avg.		&0.959     	&0.959     &0.919   	&0.959   &0.939     					&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the echocardiogram dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 0 & 93\\
\hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 0 & 4 \\
b=1 & 1 & 92\\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:echo:bayes:1c}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
 & a &	b \\
\hline
a=0 & 3 & 1 \\
b=1 & 9 & 84\\
\hline
\end{tabular}
\caption{Confusion matrix for kNN}
\label{tab:echo:bayes:2c}
\end{table}
\FloatBarrier
\paragraph{}Also the detailed accuracy table \ref{tab:echo:bayes:2d} shows that this approach gained a high recall with a low precision for alive-at-1 = 0 and both high precision and recall for alive-at-1 = 1.

@@

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure \\
	\midrule
	Decision Tree &  0.959   & 0.959   & 0.919     & 0.959  & 0.939           \\ 
  Random Forest &		 0.948   &  0.72    &  0.942     &  0.948  &  0.945             \\ 
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}
\FloatBarrier

@@

	Weighted Avg.   & 0.849    & 0.343     &0.842   		&0.849   &0.842     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the adult dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
              &    a &     b \\
\hline
 a = >50k      & 4454 &  3387 \\
 b = $\leq$50k & 1531 & 23189\\
\hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
\hline
              &    a &     b \\
\hline
 a = >50k      & 6321 &1520   \\
 b = $\leq$50k & 4025 &20695 \\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:adult:bayes:1c}
\end{table}
\FloatBarrier
\paragraph{}By using different discretizers and also do not seperately discretize in the preprocessing section of weka but instead let the NaiveBayers classifier use it's own discretizers namely KernelEstimator or SupervisedDiscretizer the outcome of precision and recall differ a bit by 0.05 to 0.1 higher and lower. It does obviously do not really make a difference.

@@

	Weighted Avg.   &0.835     &0.331      &0.829     &0.835     &0.831     \\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the adult dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|ll|}
	\hline
	 &              a    & b     \\
	\hline
    a = >50K      &	4647 & 3194  \\
    b = $\leq$50K & 2186 & 22534 \\
    \hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure  \\
	\midrule
	Decision Tree		& 0.86    	& 0.307   	& 0.854   & 0.86   & 0.855     \\
  Random Forest		& 0.859   	& 0.333   	& 0.853   & 0.859  & 0.851    \\
  Naive Bayes		 	&  0.83    & 0.186   & 0.854     & 0.83   & 0.837     \\
  SVM							& 0.849    	& 0.343     &0.842   	&0.849   &0.842     \\
  kNN							&0.835     	&0.331      &0.829    &0.835   &0.831			\\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the adult dataset}
\end{table}
\FloatBarrier

@@

\begin{table}[htb]
\centering
\begin{tabular}{lllllll}
	\toprule
	&								TP Rate   	&FP Rate   &Precision   &Recall  &F-Measure     	&Class\\ 
	\midrule
									&0.583     	&0.355     &0.55      	&0.583   &0.566   		    	&1\\
                 	&0.393     	&0.181     &0.389     	&0.393   &0.391      	    	&2\\
                 	&0.444     	&0.252     &0.484     	&0.444   &0.463      	    	&3\\
	Weighted Avg.   &0.492     	&0.28      &0.491     	&0.492   &0.491     			&\\
	\bottomrule
\end{tabular}
\caption{Results of the SVM-classification for the contraception dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
	\hline
	      &a   &b   &c \\
	\hline
	a = 1 &367 &105 &157 \\
 	b = 2 &117 &131 &85 \\
 	c = 3 &183 &101 &227 \\
  \hline
\end{tabular}
\caption{Confusion matrix for SVM}
\end{table}
\FloatBarrier

@@

	Weighted Avg.   &0.489     	&0.284     &0.487     	&0.489   &0.488      				&\\
	\bottomrule
\end{tabular}
\caption{Results of the kNN-classification for the contraception dataset}
\end{table}
\FloatBarrier
\vspace{6pt}

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
	\hline
	      &a   &b   &c \\
	\hline
    a = 1 &358 &99  &172\\
    b = 2 &99  &138 &96 \\
 	c = 3 &197 &90  &224 \\
  \hline
\end{tabular}
\caption{Confusion matrix for kNN}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|lll|}
\hline
              &   a &   b &   c  \\
\hline
 a = 1        & 327 & 141 & 161  \\
 b = 2        &  61 & 175 &  97  \\
 c = 3        & 127 & 138 & 246  \\
\hline
\end{tabular}
\caption{Confusion matrix for Naive Bayes}
\label{tab:contra:bayes:1c}
\end{table}
\FloatBarrier

@@

\begin{table}[h]
\centering
\begin{tabular}{lllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure   \\
	\midrule
	Decision Tree 	&  0.558   & 0.243   & 0.557     	& 0.558  & 0.557     \\
  Random Forest		&  0.556   & 0.241   & 0.562     	& 0.556  & 0.556     \\
  Naive Bayes		 	&  0.508   & 0.243   & 0.528     	& 0.508  & 0.513 \\
  SVM							& 0.492    &0.280     &0.491     	&0.492   & 0.491 		 \\
  kNN							&0.489     &0.284    &0.487     	& 0.489  & 0.488 		 \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the contraceptive method choice dataset}
\end{table}
\FloatBarrier\bibliography{references}
